Population Differentiation Analysis

### 2017-10-02 doc/RMD/pop-diff.Rmd
remove parallelization for reproducibility
The parallelization here did not give consistent
results, ranging from 20 to 24 PCs. By setting it to
one thread, we retain the reproducibility.

```{r dapc-region-calc, fig.width = 8, fig.height = 7, cache = TRUE}
set.seed(2017-07-05)
region.xval <- xvalDapc(tab(dat11cc), strata(dat11cc)$Region, n.pca = 15:25, 
                        n.rep = 100, parallel = "multicore", ncpus = 4)
region.dapc <- region.xval$DAPC
```

>>>>

```{r dapc-region-calc, fig.width = 8, fig.height = 7, cache = TRUE}
set.seed(2017-07-05)
region.xval <- xvalDapc(tab(dat11cc), strata(dat11cc)$Region, n.pca = 15:25, 
                        n.rep = 100)
region.dapc <- region.xval$DAPC
```
